
\documentclass[line,margin]{cv}
\usepackage{changepage}
\usepackage{hyperref}
\usepackage{xcolor}

\begin{document}

% HEADER
\name{Alexander James Wallar}
\address{Email: \href{mailto:wallar@mit.edu}{wallar@mit.edu}
\\Website: \href{http://wallar.me}
{http://wallar.me}, Phone: +1 240-470-8493}
\address{32 Vassar St. Room 376, Cambridge, MA 02139}

% BODY
\begin{resume}

% \section{Summary}
%
% I am a Ph.D.\ student in the Distributed Robotics Laboratory at MIT
% where I have been awarded the School of Engineering Lemelson
% Presidential Fellowship and the Office of the Dean of Graduate Education
% Diversity Fellowship. Previously, I was a student contractor in the Distributed
% Autonomous Systems Group at the Naval Center for Applied Research in Artificial
% Intelligence. I received a First Class Honours degree in computer science from
% the University of St Andrews in Scotland. I am an American citizen.

\section{Education}

Ph.D.\ Electrical Engineering and Computer Science
\hfill Sept 2017 -- present\\
\textbf{Massachusetts Institute of Technology}, Cambridge, MA\\
Advisor: Prof. Daniela Rus

S.M.\ Electrical Engineering and Computer Science
\hfill Sept 2015 -- June 2017\\
\textbf{Massachusetts Institute of Technology}, Cambridge, MA\\
Advisor: Prof. Daniela Rus\\
GPA: 5.0/5.0

% \begin{adjustwidth}{2.5em}{2.5em}
%
%     Working under the supervision of Dr.\ Daniela Rus as part of the
%     Distributed Robotics Laboratory working on algorithms for multi-agent
%     collision avoidance in cluttered dynamic environments. Receiving the School
%     of Engineering Lemelson Presidential Fellowship and the Office of the Dean
%     of Graduate Education Diversity Fellowship.
%
% \end{adjustwidth}

B.Sc.\ (Honours) Computer Science
\hfill Sept 2012 -- June 2015 \\
\textbf{University of St Andrews}, St Andrews, Scotland\\
First Class Honours Degree Classification
% Direct Entry Into Second Year

% \begin{adjustwidth}{2.5em}{2.5em}
%
%     First class honours degree. Direct entry into second year.\\ Dissertation
%     Title: Generating Safe Trajectories in Stochastic Dynamic Environments by
%     Leveraging Information About Obstacle Motion.
%
% \end{adjustwidth}

% International Baccalaureate Diploma
% \hfill September 2011 -- June 2012 \\
% George Mason High School \hfill Falls Church, Virginia
% \begin{adjustwidth}{2.5em}{2.5em}
%
%     Extended Essay Title: To What Extent Can Numbers of Different Bases be Used
%     to Hide Information Effectively?
%
% \end{adjustwidth}

\section{Experience}

% Graduate Student
% \hfill September 2015 -- Present \\
% Massachusetts Institute of Technology \hfill Cambridge, MA, USA
%
% \begin{adjustwidth}{2.5em}{2.5em}
%
%     Working as part of the Distributed Robotics Laboratory working on collision
%     avoidance in cluttered dynamic environments
%
% \end{adjustwidth}

Research Scientist Intern
\hfill May 2016 -- Aug 2016 \\
Research and Development Group\\
\textbf{Amazon Robotics}, Boston
\begin{itemize}

    \item Analyzed and developed algorithms for drive prioritization
        in order to reduce floor congestion

\end{itemize}

Research Scientist (Contractor)
\hfill Jan 2015 -- Aug 2015 \\
Distributed Autonomous Systems Group\\
\textbf{Naval Research Laboratory}, Washington DC
\begin{itemize}

    \item Developed algorithms for multi-agent persistent surveillance of
        risk sensitive areas

\end{itemize}

Undergraduate Research Assistant
\hfill Aug 2013 -- Aug 2015 \\
Computational Robotics Laboratory \\
\textbf{The Catholic University of America}, Various Locations
\begin{itemize}

    \item Developed path planning algorithms for swarms

\end{itemize}

%
% \begin{adjustwidth}{2.5em}{2.5em}
%
%     Worked as part of the Computational Robotics Laboratory developing
%     algorithms for swarm manipulation that seek to enable a group of unmanned
%     aerial vehicles to provide surveillance over a given region. Also created
%     path planning algorithms for swarms that generate paths through cluttered
%     dynamic environments.
%
% \end{adjustwidth}

% \newpage

Research Intern
\hfill May 2014 -- Aug 2014 \\
Distributed Autonomous Systems Group\\
\textbf{Naval Research Laboratory}, Washington DC
\begin{itemize}

    \item Developed algorithms for persistent surveillance and
        collision avoidance

\end{itemize}

% Research Assistant
% \hfill February 2014 -- October 2015 \\
% School of Computer Science, University of St Andrews \hfill St Andrews,
% Scotland
%
% \begin{adjustwidth}{2.5em}{2.5em}
%
%     Worked with Dr.\ Juan Ye to develop computer vision techniques to produce
%     haptic feedback from two dimensional images.
%
% \end{adjustwidth}
%
% Research Assistant
% \hfill September 2013 -- June 2014 \\
% School of Psychology, University of St Andrews \hfill St Andrews, Scotland

% \begin{adjustwidth}{2.5em}{2.5em}
%
%     Configured a novel experimental setup that involves three active-shutter 3D
%     displays of different sizes that can be viewed simultaneously through beam
%     splitters.
%
% \end{adjustwidth}

NSF Research Intern
\hfill May 2013 -- Aug 2013 \\
Experiment Research in Wireless Networking Group\\\textbf{University of Notre Dame}, South Bend
\begin{itemize}
    \item Created a JavaScript library for in-browser eye tracking and gaze prediction
\end{itemize}


% High School Research Intern
% \hfill July 2012 -- August 2012 \\
% The Catholic University of America \hfill Washington DC, USA
%
% \begin{adjustwidth}{2.5em}{2.5em}
%
%     Created an interface for controlling an iRobot Create using voice commands
%     spoken to an Android enabled device. Also developed algorithms for swarm
%     path planning that enabled a group of robots to move from an initial
%     configuration to a goal configuration.
%
% \end{adjustwidth}

% Intern
% \hfill July 2011 -- August 2011 \\
% Embassy of the United States \hfill Bucharest, Romania
%
% \begin{adjustwidth}{2.5em}{2.5em}
%
%     Worked with the Financial Management Office to provide assistance including
%     managing spreadsheets for payment and shredding papers.
%
% \end{adjustwidth}

% \subsubsection{Hackathons}
%
% \begin{itemize}
%
%     \item Second place, KCL Tech Society HackKing's Hackathon
%     \item Finalist, Barclays Openminds Hackathon
%     \item First place, J.P.\ Morgan Code for Good Hackathon
%     \item Second place, University of Edinburgh Security Appathon
%     \item Third place, University College London Hackin' the City
%
% \end{itemize}

% \section{Professional Affiliations}
%
% \begin{itemize}
%
%     \item Student Member, IEEE \hfill Nov '14 -- Present
%     \item Student Member, IEEE Computational Intelligence Society
%         \hfill Nov '14 -- Present
%     \item Student Member, IEEE Robotics and Automation Society
%         \hfill Mar '15 -- Present
%
% \end{itemize}

% \section{Positions of Responsibility}
%
% \begin{itemize}
%
%     \item Class Representative, University of St Andrews
%         \hfill September 2014 -- May 2015
%     \item President, St Andrews Computing Society
%         \hfill May 2013 -- June 2014
%
% \end{itemize}
%
% \section{Technical Interests}
%     Swarm Robotics, Emergent Behaviour, Complex Systems, Autonomous
%     Systems, Path Planning, Aerial Robotics, Artificial Intelligence,
%     Computational Intelligence, Evolutionary Algorithms, Robotic Middleware,
%     Stochastic Planning, Sampling Based Motion Planning, Evolutionary Robotics,
%     Swarm Intelligence, Consensus Filtering, Mapping, Surveillance, Search \&
%     Rescue, Game Theory, Computational Geometry, Collision Avoidance
%
% \section{Programming Languages}
%     Python, C, C++, Java, JavaScript, Matlab, Go, C\#, Maple,
%     Mathematica, Haskell \\
%
% \section{Programming Libraries}
%     ROS, OpenCV, ZeroMQ, Flask, NumPy, Matplotlib, OpenKinect, SciPy,
%     Scikit-Learn\\
%
\section{Publications}

\begin{enumerate}

    \item \textbf{A. Wallar}, B. Araki, R. Chang, J. Alonso-Mora, and D. Rus (2017):
        Foresight: Remote Sensing For Autonomous Vehicles Using a Small Unmanned Aerial Vehicle.
        \textit{Field and Service Robotics}, in press

    \item J. Alonso-Mora, \textbf{A. Wallar}, and D. Rus (2017): Predictive Routing for Autonomous
        Mobility-On-Demand Systems with Ride-Sharing.
        \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, in press

    \item J. Alonso-Mora, S. Samaranayake, \textbf{A. Wallar},
        E. Frazzoli, and D. Rus (2017): On-demand High-capacity Ride-sharing via Dynamic Trip-vehicle
        Assignment.
        \textit{Proceedings of the National Academy of Sciences}, vol. 114, no. 3, pp. 462--467

    \item \textbf{A. Wallar}, E. Plaku, and D. Sofge (2015):
        Reactive Motion Planning for Unmanned Aerial Surveillance
        of Risk-Sensitive Areas. \textit{IEEE Transactions on Automation Science
    and Engineering}, vol. 12, issue 3, pp. 969 -- 980

    \item D. Sofge, N. Sydney, \textbf{A. Wallar}, and K. Sullivan (2015):
        Mobile Autonomous Navy Teams for Information Surveillance
        and Search (MANTISS). \textit{Naval Research Laboratory Review}, pp. 155--157

    \item \textbf{A. Wallar} and E. Plaku (2014): Path Planning for
        Swarms in Dynamic Environments by Combining Probabilistic Roadmaps
        and Potential Fields. \textit{IEEE Symposium on Swarm Intelligence}

    \item \textbf{A. Wallar}, E. Plaku, and D. Sofge (2014): A Planner
        for Autonomous Risk-Sensitive Coverage (PARCov) by a Team of Unmanned
        Aerial Vehicles. \textit{IEEE Symposium on Swarm Intelligence}

    \item \textbf{A. Wallar} A and E. Plaku (2014): Path Planning for
        Swarms by Combining Probabilistic Roadmaps and Potential Fields.
        \textit{Springer LNAI Towards Autonomous Robotic Systems}, vol. 8069,
        pp. 417 -- 428

\end{enumerate}

\section{Theses}

\begin{enumerate}


    \item \textbf{A. Wallar} (2017): On-demand High-capacity Ride-sharing via
        Dynamic Trip-Vehicle Assignment with Rebalancing. S.M.\ Thesis.
        Massachusetts Institute of Technology

    \item \textbf{A. Wallar} (2015): Generating Safe Trajectories
        in Stochastic Dynamic Environments by Leveraging Information About
        Obstacle Motion. Undergraduate Thesis. University of St Andrews

\end{enumerate}

% \newpage

\section{Posters \& Presentations}

\begin{enumerate}

    \item N. Sydney, \textbf{A. Wallar}, D. Sofge (2015):
        Distributed Information-Theoretic Target Detection Using
        Physics-Inspired Motion Coordination.
        \textit{8th International Symposium on
        Resilient Control Systems}

    \item \textbf{A. Wallar}, E. Plaku, and D. Sofge (2014): Risk
        Sensitive Surveillance with Optimal Sensor Quality for Distributed
        Robotic Systems. \textit{Entrepreneur First UnHacked}

    \item \textbf{A. Wallar} A, C. Poellabauer, A. Sazonovs, and P. Flynn (2014):
        Camgaze.js: A JavaScript Library for Eye Tracking and Gaze
        Prediction. \textit{Edinburgh University Young Scientific Researchers
        Association (EUYSRA) Conference}

    \item \textbf{A. Wallar}, C. Choi, and A. Sazonovs (2013): Bowtie:
        In-browser Mobile Aided Sensor Acquisition using HTML5.
        \textit{Scottish Informatics and Computer Science Alliance
        (SICSA) DemoFest}

    \item \textbf{A. Wallar}, C. Poellabauer, A. Sazonovs, and P. Flynn (2013):
        Camgaze.js: A JavaScript Library for Eye Tracking. \textit{Scottish
        Informatics and Computer Science Alliance (SICSA) DemoFest}

\end{enumerate}

\section{Awards}

- School of Engineering Lemelson Presidential Fellowship, MIT, 2015 -- 16\\
- Office of the Dean of Graduate Education Diversity Fellowship, MIT, 2015 -- 16\\
- Best Paper Award Nominee, Symposium Series on Computational Intelligence, 2014
- Dean's List, University of St Andrews, 2012 -- 15\\
- Best Poster Prize, University of Notre Dame NSF REU Conference, 2013\\
- Winner, J.P.\ Morgan Code for Good Hackathon, 2013

% \section{Publication Reviewing}
% International Conference on Robotics and Automation\\
% International Symposium on Distributed Autonomous Robotic Systems

\section{Courses}

\textbf{Massachusetts Institute of Technology}:
Advances in Computer Vision, Advanced Algorithms, Computer Networks,
User Interface Design and Implementation

\textbf{University of St Andrews}:
Foundations of Computation (Accelerated), Advanced Programming Projects,
Advanced Computer Science, Discrete Mathematics, Software Engineering,
Data Encoding, Operating Systems, Computational Complexity,
Artificial Intelligence, Component Technology, Major Software Team Project,
Video Games, Artificial Intelligence Practice, Logic and Software Verification,
Knowledge Discovery and Data Mining, Distributed Systems, Constraint Programming,
Major Software Project

\section{Programming Languages and Tools}

Python, Java, C++, C, JavaScript, Go, MATLAB \\
ROS, RethinkDB, Flask, ZeroMQ

\end{resume}
\end{document}
